Return of the Linguist:\\Toward scalable parallel corpus generation for machine translation

### 2016-06-03 doc/paper.tex
a halfway presentable abstract

% emnlp2016.sty, included by header-emnlp.tex, does NOT tolerate ANY surrounding \else statements...
% an if/else if/... or ifcase statement would have been preferred...
% but \documentclass is declared in the header file, which results in some hidden error-checking:
    % unsupported \buildtarget will fail to build (``\usepackage before \documentclass'')
    % duplicate target values (e.g., emnlp=amta=0) will fail to build (``two \documentclass commands'')
\if \buildtarget \buildemnlp    
    \input{header-emnlp.tex}
    \newcommand\mycitep[1]{\cite{#1}}     % conference-specific ``glue code''
    \newcommand\mynewcite[1]{\newcite{#1}}
    \newcommand\amtaonly[1]{#1} % currently being used to trim down to 4 pages
    \newcommand\emnlponly[1]{#1}
    \newcommand\hcomponly[1]{}
\fi
\if \buildtarget \buildamta    
    \input{header-amta.tex}
    \newcommand\mycitep[1]{\citep{#1}} 
    \newcommand\mynewcite[1]{\cite{#1}}  
    \newcommand\amtaonly[1]{#1}
    \newcommand\emnlponly[1]{}
    \newcommand\hcomponly[1]{}
\fi
\if \buildtarget \buildhcomp    
    \input{header-aaai.tex}
    \newcommand\mycitep[1]{\cite{#1}} 
    \newcommand\mynewcite[1]{\citeauthor{#1}~\shortcite{#1}}  
    \newcommand\amtaonly[1]{}
    \newcommand\emnlponly[1]{}
    \newcommand\hcomponly[1]{#1}
\fi

@@

\begin{abstract}
\amtaonly{UNDER CONSTRUCTION}

The large-scale generation of high-quality synthetic parallel corpora for data-driven machine translation is proposed.

A preliminary system for doing this is presented, striving toward syntactic complexity, in the spirit of rule-based machine translation, and high-quality sentence pairs via templates, in the spirit of example-based machine translation.

Early results have yet to show improvement. [This is because we need to scale up?]
Future work is proposed. 
We believe this is particularly amenable to crowdsourcing by ``amateur linguists.''

\end{abstract}

@@

\caption{
    (Left) Chinese-to-English BLEU scores for our baseline Moses configuration with phrase and reordering tables trained on a random 25\% subset of the IWSLT15 training corpus and interpolated (+) with tables for the remaining 75\% (\textasciitilde 150K) of the in-domain corpus, the MultiUN corpus (a \textasciitilde 1M line subset), and a synthetic corpus from our generator (\textasciitilde 5M lines).
    (Right) Same as on the left, but starting with tables for the entire IWSLT15 corpus.
    Official published scores of the IWSLT15 baseline system are also given for comparison.    
    Qualitatively similar trends for NIST and TER scores were also observed (omitted for clarity).
%    The ``baseline'' row gives 
%    MultiUN is actually more data because it has more words per line.
% automatically cleaned version of the en-zh_zh language pair of OpenSubtitles 2016, roughly 1M lines.
% and a similar number of lines from MultiUN, which is actually more words. but it doesn't do as well.
} % caption

>>>>

% emnlp2016.sty, included by header-emnlp.tex, does NOT tolerate ANY surrounding \else statements...
% an if/else if/... or ifcase statement would have been preferred...
% but \documentclass is declared in the header file, which results in some hidden error-checking:
    % unsupported \buildtarget will fail to build (``\usepackage before \documentclass'')
    % duplicate target values (e.g., emnlp=amta=0) will fail to build (``two \documentclass commands'')
\if \buildtarget \buildemnlp    
    \input{header-emnlp.tex}
    \newcommand\mycitep[1]{\cite{#1}}     % conference-specific ``glue code''
    \newcommand\mynewcite[1]{\newcite{#1}}
    \newcommand\amtaonly[1]{} % currently being used to trim down to 4 pages
    \newcommand\emnlponly[1]{#1}
    \newcommand\hcomponly[1]{}
\fi
\if \buildtarget \buildamta    
    \input{header-amta.tex}
    \newcommand\mycitep[1]{\citep{#1}} 
    \newcommand\mynewcite[1]{\cite{#1}}  
    \newcommand\amtaonly[1]{#1}
    \newcommand\emnlponly[1]{}
    \newcommand\hcomponly[1]{}
\fi
\if \buildtarget \buildhcomp    
    \input{header-aaai.tex}
    \newcommand\mycitep[1]{\cite{#1}} 
    \newcommand\mynewcite[1]{\citeauthor{#1}~\shortcite{#1}}  
    \newcommand\amtaonly[1]{}
    \newcommand\emnlponly[1]{}
    \newcommand\hcomponly[1]{#1}
\fi

@@

% TODO: follow the 300-word website limit as a guideline to abstract length? check pdf guide
\begin{abstract}
The large-scale generation of synthetic parallel corpora for data-driven machine translation is proposed.
A rudimentary system for doing this is presented, with mechanisms for syntactic complexity in the spirit of classical rule-based machine translation and high-quality sentence pairs in the spirit of example-based machine translation.
Preliminary experiments integrating these synthetic corpora into a shared task are reported.
Promising future directions are discussed, in particular, large-scale contributions from ``amateur linguists'' via crowdsourcing.
\end{abstract}

@@

% TODO: mention that official results are on a slightly different Moses configuration? mehhhhh
\caption{
    (Left) Chinese-to-English BLEU scores for our baseline Moses configuration with phrase and reordering tables trained on a random 25\% subset of the IWSLT15 training corpus and interpolated (+) with tables for the remaining 75\% (\textasciitilde 150K) of the in-domain corpus, the MultiUN corpus (a \textasciitilde 1M line subset), and a synthetic corpus from our generator (\textasciitilde 5M lines).
    (Right) Same as on the left, but starting with tables for the entire IWSLT15 corpus.
    Official published scores of the IWSLT15 baseline system are also given for comparison.    
    Qualitatively similar trends for NIST and TER scores were also observed (omitted for clarity).
%    The ``baseline'' row gives 
%    MultiUN is actually more data because it has more words per line.
% automatically cleaned version of the en-zh_zh language pair of OpenSubtitles 2016, roughly 1M lines.
% and a similar number of lines from MultiUN, which is actually more words. but it doesn't do as well.
} % caption
